Multi-task learning in Computer Vision

### 2020-05-31 5-Multitask.tex
More image fixes

\begin{figure}[h!] 
\centering 
\includegraphics[width=1\textwidth]{imgs/multipleShares.png}
\caption{Many ways of sharing between tasks. Figure from \citep{healthyDrink}.\label{fig:params}}
\end{figure}

>>>>

\begin{figure}[h!] 
\centering 
\includegraphics[width=1\textwidth]{imgs/multipleShares.png}
\caption{Some ways of sharing features between tasks. Here the global features are from resnet. The fc blocks are fully-connected heads. B1 is one ResNet block and B2 is two ResNet blocks. Out of these model F was the best. Figure adapted from \citep{healthyDrink}.\label{fig:params}}
\end{figure}

### 2020-05-31 HY-CS-main.tex
More image fixes

%% OPTIONAL STEP: Set up properties and metadata for the pdf file that pdfLaTeX makes.
%% Your name, work title, and keywords are recommended.
\hypersetup{
    unicode=true,           % to show non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Multi-task learning in Computer Vision},            % title
    pdfauthor={Konsta Kutvonen},           % author
    pdfsubject={},          % subject of the document
    pdfcreator={},          % creator of the document
    pdfproducer={pdfLaTeX}, % producer of the document
    pdfkeywords={something} {something else}, % list of keywords for
    pdfnewwindow=true,      % links in new window
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

@@

\begin{otherlanguage}{english}
    \begin{abstract}
        With modern computer vision algorithms, it is possible to solve many different kinds of problems, such as image detection, image classification, and image segmentation.
        In some cases, like in the case of a camera-based self-driving car, the task can't yet be adequately solved as a direct mapping from image to action with a single model.
        In such situations, we need more complex systems that can solve multiple computer vision tasks to understand the environment and act based on it for acceptable results.
        Training each task on their own can be expensive in terms of storage required for all weights and especially for the inference time as the output of several large models is needed.
        Fortunately, many state-of-the-art solutions to these problems use Convolutional Neural Networks and often feature some ImageNet backbone in their architecture.
        With multi-task learning, we can combine some of the tasks into a single model, sharing the convolutional weights in the network.
        Sharing the weights allows for training smaller models that produce outputs faster and require less computational resources, which is essential, especially when the models are run on embedded devices with constrained computation capability and no ability to rely on the cloud.

>>>>

%% OPTIONAL STEP: Set up properties and metadata for the pdf file that pdfLaTeX makes.
%% Your name, work title, and keywords are recommended.
\hypersetup{
    unicode=true,           % to show non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Multi-task learning in Computer Vision},            % title
    pdfauthor={Konsta Kutvonen},           % author
    pdfsubject={},          % subject of the document
    pdfcreator={},          % creator of the document
    pdfproducer={pdfLaTeX}, % producer of the document
    pdfkeywords={multi-task learning} {computer vision}, % list of keywords for
    pdfnewwindow=true,      % links in new window
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

@@

\begin{otherlanguage}{english}
    \begin{abstract}
        With modern computer vision algorithms, it is possible to solve many different kinds of problems, such as object detection, image classification, and image segmentation.
        In some cases, like in the case of a camera-based self-driving car, the task can't yet be adequately solved as a direct mapping from image to action with a single model.
        In such situations, we need more complex systems that can solve multiple computer vision tasks to understand the environment and act based on it for acceptable results.
        Training each task on their own can be expensive in terms of storage required for all weights and especially for the inference time as the output of several large models is needed.
        Fortunately, many state-of-the-art solutions to these problems use Convolutional Neural Networks and often feature some ImageNet backbone in their architecture.
        With multi-task learning, we can combine some of the tasks into a single model, sharing the convolutional weights in the network.
        Sharing the weights allows for training smaller models that produce outputs faster and require less computational resources, which is essential, especially when the models are run on embedded devices with constrained computation capability and no ability to rely on the cloud.
